Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-02-07 sections/abstract.tex
Reformatted the main tex file for customization, and changed the sections to match requirements
Adding the units package, using \unit[]{} everywhere
This is a way to make numbers with units behave better. Without it,
you can end up in annoying situations where a linebreak happens
between the numbers and the units. This keeps them together, and it
lets you do things like have fractional units like m/s.

We present radio telescope observations of the 08 April 2024 total solar eclipse from the University of 
Central Arkansas campus in Conway, Arkansas using a 2.3-m SPIDER 230C parabolic radio telescope tuned 
to a frequency of 1420 MHz. Observations began approximately 19 minutes before first contact, and ended 
approximately 2.5 minutes after fourth contact, tracking the sun across the sky using a German equatorial 
mount. Our observations show a reduction in relative radio intensity from the beginning of the lightcurve 
to the middle of totality of approximately 70\%. In our current work, we aim to compare this radio 
lightcurve with theoretical lightcurves of the eclipse as observed from our location, as well as a 
relative optical lightcurve derived from the archived livestream of the eclipse broadcast by the 
University of Central Arkansas observatory. Our goal is to compare these observations in order to 
determine the relative size of the optical and radio sun.

>>>>

We present radio telescope observations of the 08 April 2024 total solar eclipse from the University of Central Arkansas campus in Conway, Arkansas using a \unit[2.3]{m} SPIDER 230C parabolic radio telescope tuned to a frequency of \unit[1420]{MHz}.
Observations began approximately \unit[19]{min} before first contact, and ended approximately \unit[2.5]{min} after fourth contact, tracking the sun across the sky using a German equatorial mount.
Our observations show a reduction in relative radio intensity from the beginning of the lightcurve to the middle of totality of approximately 70\%.
In our current work, we aim to compare this radio lightcurve with theoretical lightcurves of the eclipse as observed from our location, as well as a relative optical lightcurve derived from the archived livestream of the eclipse broadcast by the University of Central Arkansas observatory.
Our goal is to compare these observations in order to determine the relative size of the optical and radio sun.
